\textbf{Comparing and Analyzing the Effectiveness of Various String Matching Algorithms Across Different Domains}

### 2023-10-20 main.tex
.

\documentclass{article}

\input{structure.tex} % Include the file specifying the document structure and custom commands

@@

\title{\textbf{An Investigation into Quantitatively Predicting Reading Preferences}} % Title of the assignment

\author{Math AI HL - Rahma Ammiche} % Author name and email address

\date{Words: ???} % University, school and/or department name(s) and a date

@@

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\section{Introduction} % Unnumbered section

Waffle, waffle, waffle. dgdgd

% Math equation/formula
\begin{equation}
	I = \int_{a}^{b} f(x) \; \text{d}x.
\end{equation}

Anddddd surprise! More waffle. Just with a cheeky equation to spice things up.

\begin{info}[Reflection:] % Information block
	Waffle about my sins and wrongdoings. 
\end{info}

\subsection{Aims}
If any.

\subsection{Rationale}
Here I attempt to explain the absolutely unreasonable reasons for which I would want to carry out an investigation like this.

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------

\section{Problem title} % Numbered section

In hac habitasse platea dictumst. Curabitur mattis elit sit amet justo luctus vestibulum. In hac habitasse platea dictumst. Pellentesque lobortis justo enim, a condimentum massa tempor eu. Ut quis nulla a quam pretium eleifend nec eu nisl. Nam cursus porttitor eros, sed luctus ligula convallis quis. Nam convallis, ligula in auctor euismod, ligula mauris fringilla tellus, et egestas mauris odio eget diam. Praesent sodales in ipsum eu dictum.

\subsection{Theoretical viewpoint}

>>>>

\documentclass[12pt]{article}
\usepackage{setspace}
\input{structure.tex} % Include the file specifying the document structure and custom commands

@@

\title{\textbf{Comparing and Analyzing the Effectiveness of Various String Matching Algorithms Across Different Domains}} % Title of the assignment

\author{\textbf{Research Question -} How do different string \and matching algorithms perform across various application domains, \and and what factors contribute to their varying effectiveness?} % Author name and email address

\date{\textbf{Words}: not enough} % University, school and/or department name(s) and a date

@@

\doublespacing

\maketitle % Print the title
\thispagestyle{empty}
\pagebreak
\tableofcontents
\thispagestyle{empty}

\clearpage
\pagenumbering{arabic}

\pagebreak
\section{Introduction} % Unnumbered section

The impacts and applications of string matching algorithms extend far beyond their immediate textual applications; its quotidian use in domains such as bioinformatics, web crawling and security systems make it a pertinent area of study within computer science. There is also constant research being carried out to identify more efficient algorithms, and find ways in which to combine them with other disciplines to carry out certain tasks.

For instance, multiple studies have been recently published performing various comparative analyses of new string matching algorithms [5], and their applicability to a wide range of domains such as biological sequences [6], quantum computing [7], and instrusion detection systems [8]. These findings indicate the modern-day relevance and applicability of string matching algorithms and demonstrate its worthiness as a subject of investigation.

Similarly, this paper seeks to adopt an investigative style by examining \textbf{how different string matching algorithms perform across various application domains, and the factors that contribute to their varying effectiveness}. The choice of this research question is both relevant and justifiable, reflecting the persistent demand for evaluating and optimizing string matching algorithms across a range of applications.

To examine this subject, three popular string matching algorithms were programmed and tested on their ability to carry out three tasks from three different domains. They are then evaluated on their efficiency, and applicability. To maintain focus on the research question, the reasoning and rationale behind all the decisions will be explained to demonstrate how they directly address the question.

\section{Theoretical Background} % Numbered section

\subsection{Topic Overview}

\subsection{Naive Algorithm}

\subsection{Knuth-Morris-Pratt Algorithm}

\subsection{Rabin-Karp Algorithm}

\section{Experimental Methodology}

\subsection{Research Question Decomposition}

\subsection{Measuring Performance}

\subsection{Application to Domains}

\section{Experimental Results Analysis}

\section{Conclusion}

\section{References}
